\herschel\footnote{{\it Herschel} is an ESA space observatory with science instruments provided by European-led Principal Investigator consortia and with important participation from NASA.} Orion Protostar Survey (HOPS) Imaging and Photometry Results.

### 2017-10-17 HOPS/photometry/ms.tex
wills comments one

\author{T. L. Wilson}
\affil{Naval Research Laboratory, Washington, DC, USA}

@@

A comprehensive theory of the formation of stars, which explains the origins of stars from the local raw materials and environmental conditions, is necessary for understanding processes spanning the entire range of cosmic evolution from the formation and evolution of galaxies to the formation of planets \citep{ke2012}.  Given such far-reaching significance, a primary goal of current Galactic star-formation research has been to develop such a comprehensive narrative of star formation.  This importance is further underscored by the expansive open and guaranteed-time legacy-class observing programs scheduled on major space-based observatories such as \spitzer\ \citep{spitzer}, and \herschel\ \footnote{In fact, the former name of \herschel, FIRST was an homage to one of primary objectives of \herschel: the study of the first stars and galaxies in their earliest stages.} \citep{herschel}.

@@

The  \herschel\ Orion Protostar Survey (HOPS) Open Time Key Program (PI: S. T. Megeath) was motivated by the availability of sensitive far-infrared measurements to address the challenges, (i) -- (iii), mentioned above.  HOPS uses a combination of strategies to mitigate these issues.  First, we use multi-wavelength measurements to disentangle the protostar's components.  Multi-wavelength measurements are useful because they directly connect the emergent spectral properties with the underlying physical structure and conditions of said protostar component.  As these conditions vary between the components, they also vary in the emergent emission.  Thus, the overall SED of the source may be modeled as the sum of contributions from the individual components (see, \eg, Furlan \etal\ 2016, Ali \etal\ 2010).

@@

\par
\subsection{Flux distribution functions}
\label{lfs}
\par
Figure~\ref{fig:fd}\ shows the flux distribution (FD) functions at 70~\micron\ and 160~\micron, respectively, for all sources detected in our sample.  Figures~\ref{fig:fd70regional}~\&~\ref{fig:fd160regional} show the flux distributions segregated by sub-region, and separately for the Orion~A (left column) and Orion~B (right column) clouds.  The sub-region and the number of associated sources are identified within the sub-panels of the Figures.  We do not consider upper limits in these FDs (sources with flag value = 2 in Table~\ref{tbl:obs}). There are distinct differences apparent in the observed flux distributions as a function of sub-region.  We note that in a flux-limited survey, such as ours, local environmental differences in the amount and structure of the nebular emission can significantly bias source detection and photometry algorithms.  We quantify FD differences and investigate the role of bias below.
\par
The 70~\micron\ FDs are relatively flat (\ie, the number of sources in all bins is similar) for the Orion~B sub-regions: LDN~1622, NGC~2068, and NGC~2023/4.  This situation is likely due to the low numbers of protostars available for each sub-region.  In Orion~A, the 70~\micron\ FDs have an apparent peak at or near 1 Jy in all sub-regions.  And, no significant differences are obvious between sub-regions, except for LDN~1641-N.
\par
The 160~\micron\ FDs show clear and obvious differences amongst the sub-regions.  The following results, in particular, are noted: (i) there is a complete lack of sources below $\sim$500~mJy in OMC-2/3 region.  (ii) The LDN~1641 (all) and OMC~2/3 sub-regions have apparent peaks in FDs at different flux values.  (iii) The peak of the ONC-S flux distribution is between those of LDN~1641 and OMC~2/3.  And, (iv) in Orion~B, LDN~1622 and NGC~2023/4 show differences in the observed distribution, even with the low number of sources available.
\par
The 160~\micron\ FDs suggest a trend of increasingly bright sources towards lower declinations in Orion~B, and increasingly bright sources towards higher declinations in Orion~A.  We investigate this apparent trend by plotting the median flux for each sub region as a function of declination.  Figure~\ref{fig:mdFlux_v_dec} shows the resulting quantitative correlations.  The median shows a systematic change as a function of declination (sub-region) as noted above.  The trend is, however, weakly noted in the 70~\micron\ fluxes, and shows OMC 2/3 region with significantly different median flux for the 160~\micron\ fluxes.  The implications for this result are discussed in Section~\ref{sec:discussion}.

\subsection{Flux ratio distribution}
\label{sec:fratio}
\par
Flux ratios (colors) are better suited for determining differences as a function of source type than the flux itself because flux ratios depend on the shape of the source SED \citep{ali}. We investigated two different flux ratios using the combined Spitzer, HOPS and Gould-Belt photometry: \clra, and \clrb. Figure~\ref{fig:clrclr} shows the flux-ratio vs flux-ratio plots segregated by sub-region for Orion A and Orion B. We do not include data with upper limits for these plots (sources with flag value = 2 in Table~\ref{tbl:obs}). The red symbols show the colors for the sub-region identified in the sub-panel, and the gay symbols show the colors for the entire sample. As with the median of the FD, we note an apparent systematic change in the observed flux ratios relative to the entire population in both Orion~A and Orion~B.
\par
We quantitatively explore this apparent trend further in Figures~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec}. These Figures show the mean and median colors for each of the sub-regions as a function of the mean declination for all sources belonging to the respective sub-region.  Since the sub-regions are vertically segregated in both the Orion~A and B clouds, declination is a useful proxy for sub-region.
\par
In Orion~A, the median and mean colors of the sub-regions become systematically redder towards higher declinations.  In Orion~B, the median and mean colors of the sub-regions becomes systematically redder towards lower declinations.  For both, the vertical bar shows the 1-$\sigma$\ standard deviation of the flux-ratio values as a proxy for the range.  Even with large variation in color, the systematic trends with declination is clearly delineated.

@@

Completeness limits are difficult to estimate accurately.  The detection efficiency is a strong function of the magnitude of the local nebular emission;  Hence, we expect the limits to vary considerably even within a single sub-region as the nebular emission itself varies inside any of our adopted sub-region boundaries.  This variation makes it difficult to disentangle observational bias from any real trends shown in Figures~\ref{fig:mdFlux_v_dec},~\&~\ref{fig:clrclr}.

@@

Figure~\ref{fig:clrflux} shows the observed 70~\micron\ flux as a function of the flux ratios used in our investigation.  We note a marginal dependence of 70~\micron\ flux with the \clra\ color, and no obvious correlation with \clrb.  The first trend is not surprising because the protostar flux is dominated by the envelope whose SED peaks near 70~\micron.  Indeed, 70~\micron\ flux changes likely track changes in the amount of material present in the envelope.  In addition, material deeper inside the envelope (closer to the protostar) will be warmer and, hence, will emit more brightly at 70~\micron\ than at 100~\micron\ or 160~\micron.  Therefore, we expect to notice the equivalent of a hotter black body with lesser envelope material.  The \clrb\ color samples the Rayleigh-Jeans side of the SED peak and should show only marginal variation with changing temperature.  On the other hand, the \clra\ color samples the Wien side of the SED and is more likely to show some variation.  Following this reasoning, we understand the loose correlation seen only  between 70~\micron\ flux and \clra\ in Figure~\ref{fig:clrflux}.

@@

\subsection{Population differences}
\label{sec:popdiff}
\par
We also consider the implications if the correlations shown in Figure~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec} are due to systematic differences in the observed population as a function of sub-region.  \cite{ali} show that \herschel\ colors become redder with increasing envelope mass (envelope accretion rate).  In fact, the envelope accretion rate is the dominating factor in setting colors.  We rule out inclination as a factor because no reasonable justification can be made for systematic differences in inclination as a function of sub-region in Orion.  Thus, we focus on differences in envelope properties.  When interpreted as such, Figures~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec}  imply that either the accretion process is different amongst the sub-regions, or that the protostars are at systematically different stages of development in each sub-region.   Both scenarios thereby conspire to lead to systematic differences in the envelope properties of the protostars.
\par
If we surmise that the accretion process is the leading cause, then there are two means to achieve this end: (i) the available gas and dust contributing to the envelope is systematically different between the sub-regions, or (ii) the central cores are systematically more massive in regions with redder colors.  Both scenarios may, in fact, point to simply having higher gas+dust densities and higher gas+dust content to explain redder colors.  We conclude that the observed properties of \herschel-detected protostars in Orion are consistent with predicted differences in populations implied by differences in gas column densities and star-formation scenarios in the region.
\par
Megeath et al (TOM, what reference goes here?) argue that regions with higher density may speed up protostellar evolution because collapse time-scales are dependent on the local density of material.  Thus, the observed trends in Figures~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec} may alternatively be viewed as differences in the evolutionary status of the protostars.  To explain the trend, the protostars in the Orion OMC-2/3 and ONC sub-regions are required to have transferred more of their mass in the central cores, which leads to more accretion and higher infall rates.  While similar to differences in the accretion processes, this scenarios suggests a fundamental difference in the star-formation process itself between sub-regions.

@@

\bibitem[Fischer \etal\ (2017)]{will} Fischer, W., J., \etal, 2017, ApJ, accepted for publication.

>>>>

\author{T. L. Wilson}
\affil{National Science Foundation, Arlington, VA, USA}

@@

A comprehensive theory of the formation of stars, which explains the origins of stars from the local raw materials and environmental conditions, is necessary for understanding processes spanning the entire range of cosmic evolution from the formation and evolution of galaxies to the formation of planets \citep{ke2012}.  Given such far-reaching significance, a primary goal of current Galactic star-formation research has been to develop such a comprehensive narrative of star formation.  This importance is further underscored by the expansive open and guaranteed-time legacy-class observing programs scheduled on major space-based observatories such as \spitzer\ \citep{spitzer}, and \herschel\ \footnote{In fact, the former name of \herschel, FIRST was an homage to one of primary objectives of \herschel: the study of the first stars and galaxies in their earliest stages.} \citep{herschel}.  Further, the "Birth of Stars and Protoplanetary Systems" is one of the four science themes for the James Webb Space Telescope\footnote{https://jwst.nasa.gov/science.html}.

@@

The  \herschel\ Orion Protostar Survey (HOPS) Open Time Key Program (PI: S. T. Megeath) was motivated by the availability of sensitive far-infrared measurements to address the challenges, (i) -- (iii), mentioned above.  HOPS uses a combination of strategies to mitigate these issues.  First, we use multi-wavelength measurements to disentangle the protostar's components.  Multi-wavelength measurements are useful because they directly connect the emergent spectral properties with the underlying physical structure and conditions of said protostar component.  As these conditions vary between the components, they also vary in the emergent emission.  Thus, the overall SED of the source may be modeled as the sum of contributions from the individual components (see, \eg, Furlan \etal\ 2017, Ali \etal\ 2010).

@@

\par
\subsection{Flux distribution functions}
\label{lfs}
\par
Figure~\ref{fig:fd}\ shows the flux distribution (FD) functions at 70~\micron\ and 160~\micron, respectively, for all sources detected in our sample.  Figures~\ref{fig:fd70regional}~\&~\ref{fig:fd160regional} show the flux distributions segregated by sub-region, and separately for the Orion~A (left column) and Orion~B (right column) clouds.  The sub-region and the number of associated sources are identified within the sub-panels of the Figures.  We do not consider upper limits in these FDs (sources with flag value = 2 in Table~\ref{tbl:obs}). There are distinct differences apparent in the observed flux distributions as a function of sub-region.  We note that in a flux-limited survey, such as ours, local environmental differences in the amount and structure of the nebular emission can significantly bias source detection and photometry algorithms.  We quantify FD differences and investigate the role of bias below.
\par
The 70~\micron\ FDs are relatively flat (\ie, the number of sources in all bins is similar) for the Orion~B sub-regions: LDN~1622, NGC~2068, and NGC~2023/4.  This situation is likely due to the low numbers of protostars available for each sub-region.  In Orion~A, the 70~\micron\ FDs have an apparent peak at or near 1 Jy in all sub-regions.  And, no significant differences are obvious between sub-regions, except for LDN~1641-N.
\par
The 160~\micron\ FDs show clear and obvious differences amongst the sub-regions.  The following results, in particular, are noted: (i) there is a complete lack of sources below $\sim$500~mJy in OMC-2/3 region.  (ii) The LDN~1641 (all) and OMC~2/3 sub-regions have apparent peaks in FDs at different flux values.  (iii) The peak of the ONC-S flux distribution is between those of LDN~1641 and OMC~2/3.  And, (iv) in Orion~B, LDN~1622 and NGC~2023/4 show differences in the observed distribution, even with the low number of sources available.
\par
The 160~\micron\ FDs suggest a trend of increasingly bright sources towards lower declinations in Orion~B, and increasingly bright sources towards higher declinations in Orion~A.  Since the sub-regions are segregated by declination in both the Orion~A and B clouds, declination is a useful proxy for sub-region.
We investigate this apparent trend by plotting the median flux for each sub region as a function of declination.  Figure~\ref{fig:mdFlux_v_dec} shows the resulting quantitative correlations.  The median shows a systematic change as a function of declination (sub-region) as noted above.  The trend is, however, weakly noted in the 70~\micron\ fluxes, and shows OMC 2/3 region with significantly different median flux for the 160~\micron\ fluxes.  The implications for this result are discussed in Section~\ref{sec:discussion}.

\subsection{Flux ratio distribution}
\label{sec:fratio}
\par
Flux ratios (colors) are better suited for determining differences as a function of source type than the flux itself because flux ratios depend on the shape of the source SED \citep{ali}. We investigated two different flux ratios using the combined Spitzer, HOPS and Gould-Belt photometry: \clra, and \clrb. Figure~\ref{fig:clrclr} shows the flux-ratio vs flux-ratio plots segregated by sub-region for Orion A and Orion B. We do not include data with upper limits for these plots (sources with flag value = 2 in Table~\ref{tbl:obs}). The red symbols show the colors for the sub-region identified in the sub-panel, and the gay symbols show the colors for the entire sample. As with the median of the FD, we note an apparent systematic change in the observed flux ratios relative to the entire population in both Orion~A and Orion~B.
\par
We quantitatively explore this apparent trend further in Figures~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec}. These Figures show the mean and median colors for each of the sub-regions as a function of the mean declination for all sources belonging to the respective sub-region.
\par
In Orion~A, the median and mean colors of the sub-regions become systematically redder towards higher declinations.  In Orion~B, the median and mean colors of the sub-regions becomes systematically redder towards lower declinations.  For both, the vertical bar shows the 1-$\sigma$\ standard deviation of the flux-ratio values as a proxy for the range.  Even with large variation in color, the systematic trends with declination is clearly delineated.

@@

Here, we discuss whether photometric completion limit biases our observations and produces the apparent trends discussed above.  Completeness limits are difficult to estimate accurately.  The detection efficiency is a strong function of the magnitude of the local nebular emission;  Hence, we expect the limits to vary considerably even within a single sub-region as the nebular emission itself varies inside any of our adopted sub-region boundaries.  This variation makes it difficult to disentangle observational bias from any real trends shown in Figures~\ref{fig:mdFlux_v_dec},~\&~\ref{fig:clrclr}.

@@

Figure~\ref{fig:clrflux} shows the observed 70~\micron\ flux as a function of the flux ratios used in our investigation.  We note a marginal dependence of 70~\micron\ flux with the \clra\ color, and no obvious correlation with \clrb.  The first trend is not surprising because the protostar flux is dominated by the envelope whose SED peaks near 70~\micron.  Indeed, 70~\micron\ flux changes likely track changes in the amount of material present in the envelope.  In addition, material deeper inside the envelope (closer to the protostar) will be warmer and, hence, will emit more brightly at 70~\micron\ than at 100~\micron\ or 160~\micron.  Therefore, we expect to notice the equivalent of a hotter black body with lesser envelope material.  The \clrb\ color samples the Rayleigh-Jeans side of the SED peak and should show only marginal variation with changing temperature.  On the other hand, the \clra\ color samples the Wien side of the SED and is more likely to show some variation.  Following this reasoning, we understand the loose correlation seen only  between 70~\micron\ flux and \clra\ in Figure~\ref{fig:clrflux}.  However, we note that the \clra\ is also influenced by inclination and cavity geometry, which can creates additional spread in said color ratio.

@@

\subsection{Population differences}
\label{sec:popdiff}
\par
We also consider the implications if the correlations shown in Figure~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec} are due to systematic differences in the observed population as a function of sub-region.  \cite{ali} show that \herschel\ colors become redder with increasing envelope mass (envelope accretion rate).  In fact, the envelope infall rate is the dominating factor in setting colors.  We rule out inclination as a factor because no reasonable justification can be made for systematic differences in inclination as a function of sub-region in Orion.  Thus, we focus on differences in envelope properties.  When interpreted as such, Figures~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec}  imply that either the accretion process is different amongst the sub-regions, or that the protostars are at systematically different stages of development in each sub-region.   Both scenarios thereby conspire to lead to systematic differences in the envelope properties of the protostars.
\par
If we surmise that the accretion process is the leading cause, then there are two means to achieve this end: (i) the available gas and dust contributing to the envelope is systematically different between the sub-regions, or (ii) the central cores are systematically more massive in regions with redder colors.  Both scenarios may, in fact, point to simply having higher gas+dust densities and higher gas+dust content to explain redder colors.  We conclude that the observed properties of \herschel-detected protostars in Orion are consistent with predicted differences in populations implied by differences in gas column densities and star-formation scenarios in the region.
\par
Megeath et al (TOM, what reference goes here?) argue that regions with higher density may speed up protostellar evolution because collapse time-scales are dependent on the local density of material.  Thus, the observed trends in Figures~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec} may alternatively be viewed as differences in the evolutionary status of the protostars.  To explain the trend, the protostars in the Orion OMC-2/3 and ONC sub-regions are required to have transferred more of their mass in the central cores, which leads to more accretion and higher infall rates.  While similar to differences in the accretion processes, this scenarios suggests a fundamental difference in the star-formation process itself between sub-regions.

@@

\bibitem[Fischer \etal\ (2017)]{will} Fischer, W., J., \etal, 2017, ApJ, 840, 69
